CGAT In The Hat

### 2012-12-06 paper/paper.tex
Working on implementation

>>>>

\section{Database Choice}
% TODO(ryan): Put decision and considereations here.
%  Schema will go in implementation section.
%  Incoude some text about how having the documents in JSON (Mongo is actually BSON) makes it really easy to use in JSON.

\section{Implementation}\label{sec:implementation}
CGAT uses a standard LAMP stack with MySQL traded out for MongoDB.

\subsection{Backend}
The \textit{backend} of the system consists of a PHP server connecting to a MongoDB database.
We do not use any templating systems.
We chose PHP for the backend because we did not require most of the functionality of a templating system, and we wanted a simple
system that can be easily understood when passed off to the next generation.

Mongo's PHP connecter is fully featured.
TODO(eriq): Cite mongo's php connector.

\subsubsection{Database Schema}

\subsubsection{API}
CGAT is an entireley API driven product. The API is central to all the behavior.
The API supplies \textbf{all} the information that is displayed in the UI.
This is a very important design choice. Having the API be the sole data provider and manipulator for the system
means that all functionality can be programatically provided and different applications can present the same
fuinctionality with a different UI.

The API accepts GET and PUT requests (depending on the action) and will always return a JSON response.

The current API supports 21 different calls, 7 GET requests and 14 POST actions.

\paragraph{GET Requests}
\begin{itemize}
\item administration_info - Provides the user with meta information information that the user would need to perform administrative tasks such as greating a group or assigning a task.
\item annotation - Provide the user with information about an specified annotation.
\item contig - Get information about a specific contig.
\item gene - Get information about a specific gene.
\item group - Get information about a specific group.
\item help - Get help information on a specific topic.
\item user_profile - Get the profile information about a specific user. If the user is logged in and requests information about themselves, more information is provided.
\end{itemize}

\paragraph{POST Actions}
Most POST actions require that the user is logged in.

\begin{itemize}
\item assign_task - Ask a group of people to perform an annotation.
\item cancel_notification - Clear a notification from a user.
\item create_annotation - Create a new annotation of a contig.
\item create_group - Create a group.
\item join_group - Join a group.
\item leave_group - Leave a group.
\item login - Login.
\item logout - Logout.
\item parse_fasta - Upload a FASTA file to the server, parse the contents, and returned the parsed structure.
\item register - Register a new user.
\item save_annotation - Save a work-in-progress annotation.
\item set_help - Upload a help page.
\item submit_annotation - Submit a finalized annotaion.
\item upload_contig - Uplaod a contig into CGAT.
\end{itemize}

\subsection{Frontend}

\section{UI Design}
